Some useful information of OCV for missing data

### 2018-01-25 analysis/OCVmissdataSetting.Rmd
Files commited by wflow_commit.

>>>>

### GTEx zsocre

```{r}
library(R.matlab)
Y_centered = readMat("../data/output/missingdata/GTExZsocre/example.mat")
Y = Y_centered$Ycentered
```

### MovieLens

```{r}
library(methods)
library(R.matlab)
library(Matrix)
## run the code
ml100K_data = readRDS("../data/output/missingdata/MovieLens/scale_data.rds")
MLMatrix <- sparseMatrix(i = ml100K_data[,1],
                         j = ml100K_data[,2],
                         x = ml100K_data[,3],dims = c(943,1682))
# turn this sparse matrix into matrix in r
Y = as.matrix(MLMatrix)
Y[which(Y == 0)] = NA
# writeMat("~/HG/flash/data/OCVmissflashr2/ML100K_scaled/Ydata.mat", Y = Y)
```

### denoiseR tumor data

```{r}
library(R.matlab)
Y_centered = readMat("../data/output/missingdata/DenoiseRtumor/example.mat")
Y = Y_centered$Ycentered
```

### denoiseR text data

```{r}
library(R.matlab)
## run the code
Y_centered = readMat("../data/output/missingdata/DenoiseRtext/example.mat")
Y = Y_centered$Yscaled
```

### Breast cancer data

```{r}
library(R.matlab)
## run the code
Y_centered = readMat("../data/output/missingdata/BreastCancer/example.mat")
Y = Y_centered$Y
# in the matlab package of NSF, the use the centered data by rows
N = dim(Y)[1]
P = dim(Y)[2]
Y = Y - rowMeans(Y) %*% t(rep(1,P))
```
